---
output: github_document
html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.align = "center",
  fig.width = 6,
  fig.height = 6,
  dpi = 300,
  tidy = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/README-"
)
```

## `MonitoR` package

*Under development*

___

This package provides workflows in form of `R Markdown` templates for processing monitoring data, for now mostly focusing on the analysis of audio files obtained by deploying passive acoustic monitoring (PAM) devices. The package relies on [NocMigR2](github.com/mottensmann/NocMigR2). See details there.
    
To install the package, use [devtools](https://github.com/r-lib/devtools):

```{r Install-NocMigR2, eval=FALSE}
devtools::install_github("mottensmann/MonitoR", dependencies = TRUE)
```

*`NocMigR2` depends on `warbleR` which is currently (as of 2024-07-26) missing on CRAN. If the installation above fails try:*

```{r Install-warbleR, eval=FALSE}
devtools::install_github("maRce10/warbleR")
```

Load the package once installed:

```{r load-MonitoR, warning=FALSE, results='hide'}
library(MonitoR)
```

## Templates

`MonitoR` provides RMarkdown templates to set-up post-processing and validation of audio data classified using [BirdNET-Analyzer](https://github.com/kahst/BirdNET-Analyzer). Using `RStudio` these are accessible via `File -> New File -> RMarkdown`

### birdnet

* (1) Preprocessing of audio data (renaming to datetime, removing unessary file prefixes)
* (2) Extracting results obtained by using a AI-based classifier with [BirdNET-Analyzer](https://github.com/kahst/BirdNET-Analyzer)
* (3) Archiving manually verified records to a xlsx-database

### birdnetR

* (1) Preprocessing of audio data (renaming to datetime, removing unessary file prefixes)
* (2) Running [birdnetR](https://cran.r-project.org/package=birdnetR)
* (3) Extracting results obtained by using a AI-based classifier with [birdnetR](https://cran.r-project.org/package=birdnetR)
* (4) Archiving manually verified records to a xlsx-database

### nestcamera

* (1) Preprocessing of photos (renaming to datetime and resorting)
 
